Initial Analysis

### 2020-02-11 Initial_Analysis.Rmd
Include weight

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high'))
  )

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
    # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
    # ),
    Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  filter(Total_USD > 0)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

>>>>

#### Determine Regions ezs areas

Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_EEZ = sum(Area_km2))

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(Regional_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = n_trans_spp/Size_EEZ 
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
  )

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  left_join(Regional_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    ),
     # Include the weighted method for supplementals
    Weight_Rev = Total_USD/Size_EEZ 
    Weight_Bins = cut(Weight_Rev,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Rev,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
  )
  ) %>% 
  filter(Total_USD > 0)

@@

# Label info
label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )
